Can greedy-like heuristics be useful for solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization?

### 2020-10-15 doc/paper.tex
skracen apstrakt

	\begin{abstract}
		In this paper we deal with the Weighted Orthogonal Art Gallery Problem under the regular grid discretization. We propose a novel greedy approach which is based on balancing the trade off between the total sum of guards' costs and the total number of not yet covered points from the discretization. This new approach and an existing greedy algorithm are further  hybridized with the Integer Linear programming (ILP), originally formulated for the well known Minimum Set Cover problem. Experimental results show that the proposed greedy methods is able to achieve the optimal solutions in most cases for a class of large area polygons, while for small area polygons, they achieve solutions of reasonable quality within lower runtime than the exact algorithms.
	\end{abstract}
	\maketitle

>>>>

	\begin{abstract}
This paper considers the Weighted Orthogonal Art Gallery Problem under regular grid discretization. We propose a novel greedy approach, based on balancing the trade-off between the total sum of guards' costs and the number of not-yet-covered points. This approach is hybridized with existing ILP. Experimental results show that the methods can achieve optimal solutions in most cases for a class of large-area polygons. For small-area polygons, they achieve solutions of reasonable quality within lower runtime than the exact algorithms.
	\end{abstract}
	\maketitle
